### 2012-10-16 Docs/architecture/architecture.tex
update
some refs

  Each problem in \maestro\ gets it own sub-directory under {\tt
    SCIENCE/}, {\tt TEST\_PROBLEMS/}, or {\tt UNIT\_TESTS/}.  The {\tt
    GNUmakefile} in the problem directory includes the instructions on
  how to build the executable, including what modules in {\tt extern}
  are used.  Any file that you place in a sub-directory here takes
  precedence over a file of the same name in {\tt MAESTRO/}.  This
  allows problems to have custom versions of the main
  \maestro\ routines (e.g.\ initial conditions via {\tt initdata.f90}.
  See \S~\ref{sec:makefile} for details on the build system).

@@

  \item {\tt docs/}

@@

    The various problem-setups.

@@

      Special \maestro\ problem directories that test only a single
      component of the \maestro\ algorithm.  These often have their
      own main drivers ({\tt varden.f90}) that setup and initialize
      some data structures and then call only a few of the
      \maestro\ routines.  See \S~\ref{sec:unit_tests} for details.

>>>>

@@

  \item {\tt Docs/}

@@

    The various problem-setups.  Each problem in \maestro\ gets it own
    sub-directory under {\tt SCIENCE/}, {\tt TEST\_PROBLEMS/}, or {\tt
      UNIT\_TESTS/}.  The {\tt GNUmakefile} in the problem directory
    includes the instructions on how to build the executable,
    including what modules in {\tt extern} are used.  Any file that
    you place in a sub-directory here takes precedence over a file of
    the same name in {\tt MAESTRO/}.  This allows problems to have
    custom versions of the main \maestro\ routines (e.g.\ initial
    conditions via {\tt initdata.f90}.  See \S~\ref{sec:makefile} and
    Chapter~\ref{ch:make} for details on the build system).

@@

      Special \maestro\ problem directories that test only a single
      component of the \maestro\ algorithm.  These often have their
      own main drivers ({\tt varden.f90}) that setup and initialize
      some data structures and then call only a few of the
      \maestro\ routines.  See Chapter~\ref{chapter:unit_tests} for details.
